---
title: "Data 605 Homework 12"
author: "Trishita Nath"
date: "4/25/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

The attached who_data.csv dataset contains real-world data from 2008. The variables included follow.  

* Country: name of the country
* LifeExp: average life expectancy for the country in years
* InfantSurvival: proportion of those surviving to one year or more
* Under5Survival: proportion of those surviving to five years or more
* TBFree: proportion of the population without TB.
* PropMD: proportion of the population who_data are MDs
* PropRN: proportion of the population who_data are RNs
* PersExp: mean personal expenditures on healthcare in US dollars at average exchange rate
* GovtExp: mean government expenditures per capita on healthcare, US dollars at average exchange rate
* TotExp: sum of personal and government expenditures.

```{r echo=TRUE, eval=TRUE}
# Libraries
library(ggplot2)

```

## Data Import

```{r echo=TRUE, eval=TRUE}
who_data <- read.csv('https://raw.githubusercontent.com/nathtrish334/Data-605/main/who.csv')
head(who_data)
```

1. Provide a scatterplot of LifeExp~TotExp, and run simple linear regression. Do not transform the variables. Provide and interpret the F statistics, R^2, standard error,and p-values only. Discuss whether the assumptions of simple linear regression met.

```{r echo=TRUE, eval=TRUE}
# Linear regression model
life_exp_lm <- lm(LifeExp ~ TotExp, data=who_data)

# Scatterplot
plot(LifeExp~TotExp, data=who_data, 
     xlab="Total Expenditures", ylab="Life Expectancy",
     main="Life Expectancy vs Total Expenditures")
abline(life_exp_lm)

# Summary of Linear regression model
summary(life_exp_lm)

# Residuals variability plot
plot(life_exp_lm$fitted.values, life_exp_lm$residuals, 
     xlab="Fitted Values", ylab="Residuals",
     main="Residuals Plot")
abline(h=0)

# Residuals Q-Q plot
qqnorm(life_exp_lm$residuals)
qqline(life_exp_lm$residuals)

```

**Discussion**  
The regression output, R^2, indicates that ONLY 25.77% of variation in life expectancy is explained by the total expenditure. The Standard Error is approximately 8x smaller then the corresponding coefficient. P-value is small in indicating that the total expenditure is a significant variable and hence likely to impact life expectancy. As a result, we reject the null hypothesis. F-Statistic is Very large, indicating a stronger relationship between the independent and dependent variables. The residual plot shows there is no constant variability and the residuals are not normally distributed. Hence, this model is not good enough to describe the relationship between total expenditure and life expectancy.

2. Raise life expectancy to the 4.6 power (i.e., LifeExp^4.6). Raise total expenditures to the 0.06 power (nearly a log transform, TotExp^.06). Plot LifeExp^4.6 as a function of TotExp^.06, and r re-run the simple regression model using the transformed variables. Provide and interpret the F statistics, R^2, standard error, and p-values. Which model is "better?"

```{r echo=TRUE, eval=TRUE}
# Transformation
LifeExp_by_4.6 <- who_data$LifeExp^4.6
TotExp_by_0.06 <- who_data$TotExp^0.06

# Linear regression model build
life_exp_lm_transformed <- lm(LifeExp_by_4.6 ~ TotExp_by_0.06, who_data)

# Scatterplot of dependent and independent variables
plot(LifeExp_by_4.6~TotExp_by_0.06, 
     xlab="Total Expenditures", ylab="Life Expectancy",
     main="Life Expectancy vs Total Expenditures (Transformed)")
abline(life_exp_lm_transformed)

# Summary of Linear regression model summary
summary(life_exp_lm_transformed)

# Residuals variability plot
plot(life_exp_lm_transformed$fitted.values, life_exp_lm_transformed$residuals, 
     xlab="Fitted Values", ylab="Residuals",
     main="Residuals Plot")
abline(h=0)

# Residuals Q-Q plot
qqnorm(life_exp_lm_transformed$residuals)
qqline(life_exp_lm_transformed$residuals)
```

**Discussion**  
The transformed model is a better model since the data points are more closely clustterred around the regression line of the model. R-squared value, 72.98%, is much better than the 25.77% for the first model. Hence, the response variable (life expentancy^4.6) explains the model’s variability around the mean 72.98% of the time. The p-value of the model, < 2.2e-16, is really low, hence we can confindetly reject the null hypothesis. The F-statistic,507.7, is good, but the Standard Error, 90490000, is a bit high. From the residuals plot, variability is fairly constant with a few outliers and distribution of residuals is nearly normal with some deviation at the tails. Hence, this is a fairly good model to describe the relationship and it is significantly better than the first model. From the new scatterplot, there is a clear linear relationship between transformed variables.

3. Using the results from 3, forecast life expectancy when TotExp^.06 =1.5. Then forecast life expectancy when TotExp^.06=2.5.

```{r echo=TRUE, eval=TRUE}
new_outcome <- data.frame(TotExp_by_0.06=c(1.5,2.5))
predict(life_exp_lm_transformed,new_outcome,interval="predict")^(1/4.6)
```

When TotExp^0.06=1.5, the forecasted life expectancy is 63.31 years with a 95% confidence interval between 35.94 and 73.01.
When TotExp^0.06=2.5, the forecasted life expectancy is 86.51 years with a 95% confidence interval between 81.81 and 90.43.

4. Build the following multiple regression model and interpret the F Statistics, R^2, standard error, and p-values. How good is the model?

```{r echo=TRUE, eval=TRUE}
#Linear regression
life_exp_lm_qn4 <- lm(LifeExp ~ PropMD + TotExp + TotExp:PropMD, who_data)
summary(life_exp_lm_qn4)
#Residuals plot
plot(life_exp_lm_qn4$fitted.values, life_exp_lm_qn4$residuals, xlab="Fitted Values", ylab="Residuals",
 main="Fitted Values vs.Residuals")

# Normal Q-Q plot
qqnorm(life_exp_lm_qn4$residuals)
qqline(life_exp_lm_qn4$residuals)
```

Results

Residual Standard Error is 8.765 and F-statistic is 34.49. The p-value is really low (< 2.2e-16), hence we can reject the null hypothesis. Since average life expectancy is 67.38, the SE is not terrible and F-statistics is fairly high (but lower than in the first model). R2 is only 0.3574, hence the model explains only 35.74% of variability, which is not high. P-value is nearly 0, so the relationship is not due to random variation.From the residuals plots, there is no constant variability and that residuals are not normally distributed. This is not a good model to describe the relationship. It is almost similar to the first model.

5. Forecast LifeExp when PropMD=.03 and TotExp = 14. Does this forecast seem realistic? Why or why not?

```{r echo=TRUE, eval=TRUE}
new_outcome_01 <- data.frame(PropMD=0.03, TotExp=14)
predict(life_exp_lm_qn4,new_outcome_01,interval="predict")
```

**Discussion**

Life expectancy is predicted to be 107.70 years with 95% confidence interval between 84.25 and 131.14. This prediction is unrealistic since the highest life expectancy in the WHO data is 83 years old.