---
title: "Data 605 Homework 13"
author: "Trishita Nath"
date: "5/2/2021"
output: html_document
---


1) Use integration by substitution to solve the integral below.

$$
\int { 4{ e }^{ -7x }dx } 
$$
**Solution:**  

$$
Let\ u=-7x \\
du=-7dx \\
-\frac{du}{7}=dx
$$

4 is constant now we substitute dx with du (reverse chain rule). 
$$
\frac{-4}{7} \int { { e }^{ u }du } \\
\frac{-4}{7}e^{u}+c\\
\frac{-4}{7}e^{-7x}+c
$$


2) Biologists are treating a pond contaminated with bacteria. The level of contamination is changing at a rate of
$\frac{dN}{dt}=\frac{-3150}{t^{4}}-220$ bacteria per cubic centimeter per day, where t is the number of days since treatment began. Find a function N( t ) to estimate the level of contamination if the level after 1 day was 6530 bacteria per cubic centimeter.  

**Solution:**  

We integrate the given rate function get the function for the position / level.  

The first term can be re-witten  with a negative power and then we can apply the power rule for integration.  

$$
 \int {(\frac{-3150}{t^{4}}-220)dt}\\
 \int {(-3150{t^{-4}}-220)dt}\\
  \int-3150t^{-4}dt - \int -220dt\\
  -3150\int t^{-4}dt - 220\int dt\\
  -3150 \frac{-1}{3} t^{-3} - 220t\\
N(t)=  \frac{1050}{t^{3}}-220t+c
$$

Applying the given initial conditions.  
We have N(1)=6530,hence we want to solve for the constant c:

$$
6530=  \frac{1050}{1^{3}}-220(1)+c\\
6530=1050-220+c\\
6530-1050+220=c\\
5700=c
$$

The final function becomes: 

$$
N(t)=  \frac{1050}{t^{3}}-220t+5700
$$


3) Find the total area of the red rectangles in the figure below, where the equation of the line is $f(x)=2x-9$

**Solution**

There are 4 rectangles within the closed interval [4.5,8.5]   
By inspection we calculate the area of each rectangle and then add them up. $A=l*w$

$$
A1=(1)(5.5-4.5)=1\\
A2=(1)(6.5-5.5)=3\\
A3=(1)(7.5-5.5)=5\\
A4=(1)(8.5-6.5)=7\\
A=A1+A2+A3+A4=1+3+5+7=16
$$

We can also calculate the area by integrating the given function fro 4.5 to 8.5: 

$$
\int _{ 4.5 }^{ 8.5 }{ 2x-9 } dx\\
$$

```{r}
integrand <- function(x)
  {
  2*x-9
  }
integrate(integrand, lower = 4.5, upper = 8.5)
```

4) Find the area of the region bounded by the graphs of the given equations.

$$
y=x^{2}-2x-2\\
y=x+2
$$

Lets visualize 
```{r}
fx <- function(x){ (x^2)-2*x-2 }
gx <- function(x){x+2}
plot (fx, -15, 15)
plot (gx, -5, 5, add=TRUE)
```

Lets find the points of intersection of these functions which will be the bounds of integration: 

We set f(x)=g(x) and solve for x.  

$$
x^{2}-2x-2=x+2\\
x^{2}-3x-4=0\\
(x-4)(x+1)=0\\
x=4\\
x=-1
$$
The formula for finding the area enclosed by two curves is as follows:  

$$
\int _{ a }^{ b }{ (topFunction-lowerFunction) } dx
$$

$$
\int _{ -1 }^{ 4 }{ (x+2)-(x^{2}-2x-2) } dx\\
\int _{ -1 }^{ 4 } {(x+2-x^{2}+2x+2)dx}\\
\int _{- 1 }^{ 4 } {(-x^{2}+3x+4)dx}
$$


Lets integrate and calculate using R:
```{r}
func <- function(x){  -x^{2}+3*x+4  }
## integrate the function from 0 to infinity
integrate(func, lower = -1, upper = 4)
```

5) A beauty supply store expects to sell 110 flat irons during the next year. It costs \$3.75 to store one flat iron for one year. There is a fixed cost of \$8.25 for each order. Find the lot size and the number of orders per year that will minimize inventory costs.  

**Solution**

Lets derive the cost function.  
Let x be the number of flat irons per order. The number of orders = 110/x.  
$$
Yearly\ storage\ cost=Storage cost per iron×Average number of irons stored=3.75×x/2=1.875x \\
Yearly\ ordering\ cost=Cost of each order×Number of orders=8.25×110/x=907.5/x \\
Inventory\ cost=Yearly storage cost+Yearly ordering cost=1.875x+907.5/x=C(x)
$$
To find the critical points, we derive C(x) and set C'(x)=0. We then determine which critical point minimizes C(x)

$$
C(x)=1.875x + \frac{907.5}{x}\\
C '(x)=1.875-\frac{907.5}{x^{2}}
$$
Solve for ciritcal points 

$$
0=1.875-\frac{907.5}{x^{2}} \\
\frac{907.5}{x^{2}}=1.875 \\
907.5=1.875 x^{2} \\
 x^2=\frac{907.5}{1.875} \\
 x^2=484 \\
 x = \sqrt {484} \\
 x = \pm22
$$
We take the positive value since the number of flat irons cannot be negative.

x=22 minimizes function C(x)
Number of orders = 110/22 = 5 

6) Use integration by parts to solve the integral below

$$
\int { ln(9x)x^{6}dx } 
$$

**Solution**

We apply integration by parts. dv is the term that can be integrated easily while u is the term that can be derived easily.  
$ln$ term can be derived much easier than integrated and ($x^6$) can be derived or integrated with the same ease but in this case we integrate it since we are differentiating the other term. 

$$
uv-\int vdu \\
u=ln(9x)\\
du=\frac{1}{x}dx\\
dv=x^{6}\\
v=\frac{1}{7}x^{7}
$$

Integration by parts 

$$
\frac{x^{7}ln(9x)}{7}-\int \frac{1}{7}x^{7}\frac{1}{x}dx \\
\frac{x^{7}ln(9x)}{7}-\frac{1}{7} \int \frac{x^{7}}{x}dx \\
\frac{x^{7}ln(9x)}{7}-\frac{1}{7}\int x^{6}dx \\
\frac{x^{7}ln(9x)}{7}-\frac{1}{7}(\frac{x^{7}}{7})+C \\
\frac{x^{7}ln(9x)}{7}-\frac{x^{7}}{49}+C \\
\frac{x^{7}}{49}[7ln(9x)-1]+C
$$

7) Determine whether f(x) is a probability density function on the interval 1, e6 . If not, determine the value of the definite integral

$$
f(x)=\frac{1}{6x}
$$

**Solution**

Lets evaluate the definite integral

$$
\int _{ 1 }^{ { e }^{ 6 } }{ \frac { 1 }{ 6x } dx } \\
\frac{1}{6} \int _{ 1 }^{ { e }^{ 6 } }{ \frac { 1 }{ x } dx } \\
\frac{1}{6}(ln(e^{6})-ln(1))\\
\frac{1}{6}(6-0)\\
=1
$$
Hence, f(x) is a probability density function on the closed interval [1,$e^6$]