---
title: "Data 605 Homework 10"
author: "Trishita Nath"
date: "4/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Smith is in jail and has 1 dollar; he can get out on bail if he has 8 dollars.
A guard agrees to make a series of bets with him. If Smith bets A dollars,
he wins A dollars with probability .4 and loses A dollars with probability .6.
Find the probability that he wins 8 dollars before losing all of his money if

a. he bets 1 dollar each time (timid strategy).  

We utilize the Gambler’s Ruin equation: 
The gambler starts with a stake of size s and plays until their stake reaches the value M = 0  
$$
P_{broke} = \frac{(\frac{q}{p})^z-(\frac{q}{p})^M}{(1-\frac{q}{p})^M} \\
P_{win} = 1 - P_{broke}
$$
M=8, z=1, p=0.4, and q=0.6, since the probability of Smith winning A dollars is 0.4, losing A dollars is 0.6, Smith starts with a stake of 1 (1 dollar), and it’ll be played until Smith reaches a capital of 8  

$$
= 1 - \frac{(\frac{0.6}{0.4})^1-(\frac{q}{p})^8}{(1-\frac{0.6}{0.4})^8} \\
$$
```{r}
1 - ((1.5-(1.5^8)) / (1-(1.5^8)))
```

b. he bets, each time, as much as possible but not more than necessary to
bring his fortune up to 8 dollars (bold strategy).  

Here, as a bold move, Smith bets the whole amount, upto \$8. He starts with 1 dollar and must win 3 times in a row with probability 0.4

He places \$1 and wins to get \$2. He then places the \$2 and wins, to get \$4. Finally, if he places the \$4 and wins, they make \$8.


The probability of 3 successes in a row is

```{r}
0.4 ^ 3
```


c. Which strategy gives Smith the better chance of getting out of jail?  

The bold strategy has a better chance of winning because it requires only 3 moves and has higher probability.