---
title: "Data 605 Homework 15"
author: "Trishita Nath"
date: "5/13/2021"
output:
  html_document: default
  word_document: default
  pdf_document: default
---





## Question 1  
Find the equation of the regression line for the given points. Round any final values to the nearest hundredth, if necessary.  
( 5.6, 8.8 ), ( 6.3, 12.4 ), ( 7, 14.8 ), ( 7.7, 18.2 ), ( 8.4, 20.8 )

### Solution

```{r}
x_values <- c(5.6, 6.3, 7, 7.7, 8.4)
y_values <- c(8.8, 12.4, 14.8, 18.2, 20.8)

reg_line <- lm(y_values ~ x_values)
reg_line
```

Therefore, the regression line of the linear regression model is: $y=−14.80 + 4.26x$

#### Plot of the Regression line

```{r}
plot(x_values, y_values, xlab="x", ylab="y")
abline(reg_line)
lines(c(5,9), -14.8+4.257*c(5,9), col="blue")
```

## Question 2  
Find all local maxima, local minima, and saddle points for the function given below. Write your answer(s) in the form
( x, y, z ). Separate multiple points with a comma.
$$f ( x, y ) = 24x - 6xy^2 - 8y^3$$

### Solution

Partial derivatives:

$f_x(x,y)=24−6y^2$  
$f_y(x,y)=−12xy−24y^2$  

If $24−6y2=0$  
$y^2=4\ and\ y=±2$  

If $y=2$ and $−12xy−24y^2=0$,  
then $−24x=24×4$ hence $x=−4$  
If $y=2$ and $−12xy−24y^2=0$,  
then $24x=24×4$ and $x=4$  

f(x,y):  

$f_{(4,−2)}=24×4−6×4×(−2)2−8×(−2)3=64$  

$f_{(4,−2)}=24×(−4)−6×(−4)×22−8×23=−64$  

Hence we have two critical points: $(4,−2,64)$ and $(−4,2,−64)$  

To determine if points are minimum, maximum or saddle, we use Second Derivative test:

Taking second partial derivatives:

$f_{xx}=0$  
$f_{yy}=−12x−48y$  
$f_{xy}=−12y$  

And $D(x,y)=f_{xx}f_{yy}−f_{xy}^2=−(−12y)^2=−144y^2$  

$D(x,y)<0$ for all (x,y). As a result, according to the Second Derivative Test, the above two critical point are saddle points.


## Question 3  
A grocery store sells two brands of a product, the "house" brand and a "name" brand. The manager estimates that if she sells the "house" brand for x dollars and the "name" brand for y dollars, she will be able to sell $81 - 21x + 17y$ units of the "house" brand and $40 + 11x - 23y$ units of the "name" brand.  

**Step 1.** Find the revenue function R(x,y ).

### Solution  
$R_{(x,y)} = Revenue\ from\ house\ brand  + Revenue\ from\ name\ brand$  
$R_{(x,y)} = (81- 21x + 17y)x + (40 + 11x - 23y)y$  
$R_{(x,y)} = - 21x^2- 23y^2 + 28yx + 81x + 40y$   

**Step 2.** What is the revenue if she sells the "house" brand for $2.30 and the "name" brand for $4.10?

### Solution  
```{r}
compute_revenue <- function(x,y)
  {
   rev_func = - 21*x^2 - 23*y^2  + 28*y*x + 81*x + 40*y  
   return(c(rev_func))
  }
print(paste0("Revenue = $", compute_revenue(2.30,4.10)))
```

## Question 4  
A company has a plant in Los Angeles and a plant in Denver. The firm is committed to produce a total of 96 units of a product each week. The total weekly cost is given by $C_{(x, y)} = \frac{1}{6}x^2 + \frac{1}{6}y^2 + 7x + 25y + 700$, where x is the number of units produced in Los Angeles and y is the number of units produced in Denver. How many units should be produced in each plant to minimize the total weekly cost?

### Solution  
Cost function: 
$C_{(x, y)} = \frac{1}{6}x^2 + \frac{1}{6}y^2 + 7x + 25y + 700$ \\

Number of units:
$$
x+y=96\\
x=96-y
$$

We can now convert $C_{(x, y)}$ into a univariate function:   
$$
C_{(x, y)}=\frac{1}{6}x^{2}+\frac{1}{6}y^{2}+7x+25y+700\\
=\frac{1}{6}(96-y)^{2}+\frac{1}{6}y^{2}+7(96-y)+25y+700\\
=\frac{1}{6}(1536-192y-y^2)+\frac{1}{6}y^{2}+7(96-y)+25y+700\\
C(y)=\frac{1}{3}y^{2}-14y+2908
$$

Optimize (Derivative equals zero) 
$$
C'(y)=\frac{2}{3}y-14=0\\
\frac{2}{3}y=14\\
2y=42\\
y=21
$$

Now we have: 
$x=96-y=96-21=75$  
Hence, 21 units produced in the Denver plant and 75 units in the Los Angeles plant.

## Question 5  
Evaluate the double integral on the given region.

$(\iint_R {{e}^{8x+3y})dA}$ ;$R:2\le x \le 4$ and $2 \le y \le 4$  

### Solution

$$
\iint_{2}^{4}{{e}^{8x+3y}dxdy} \\
\iint_{ 2 }^{ 4 }{ { e }^{ 8x }{e}^{3y}dxdy } \
\iint_{ 2 }^{ 4 } ({e}^{3y}) \int _{ 2 }^{ 4 }(e^{8x})dx dy \\
\iint_{ 2 }^{ 4 } ({e}^{3y})(\frac{e^{32}-e^{16}}{8})dy \\
\frac{e^{32}-e^{16}}{8}\int _{ 2 }^{ 4 } ({e}^{3y})dy \\
[ \frac{e^{32}-e^{16}}{8}][\frac{e^{12}-e^{6}}{3}] \\
\frac{e^{44}-e^{38}-(e^{28}-e^{22})}{8*3} \\
\frac{e^{44}-e^{38}-e^{28}+e^{22}}{24} \\
\frac{1}{24}(e^{44}-e^{38}-e^{28}+e^{22}) \\
\frac{1}{24}(e^{44-38-28+22}) \\
\frac{1}{24}(e^{0}) \\
\frac{1}{24}(1) \\
\frac{1}{24}
$$